---
title: "mylinreg"
author: "Suhani Ariga"
date: "'r Sys.Date()'"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{mylinreg}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(mylinreg)
```

# Linear regression
A linear regression model is computed by using the linreg function, which returns an object for S3 class.The functionality of the package are demonstrated with the "iris" dataset.

```{r}
linreg_mod <- linreg(Petal.Length~Species, data=iris)
```

# Methods

print()
The print method returns the argument and the estimates of the coefficient.

```{r}
print(linreg_mod)
```

plot()
The plot method returns two plots.One plot with Residuals vs Fitted Values and the other one the Square of Standardized residuals vs Fitted values.

```{r}
plot(linreg_mod)
```

resid()
The resid method returns the residuals of estimates.

```{r}
resid(linreg_mod)
```

coef()
The coef method returns the regression coefficients

```{r}
coef(linreg_mod)
```

summary
The summary method returns the overview of the linear regression model.

```{r}
summary(linreg_mod)
```